Paper figures

### 2020-09-17 notebooks/paper_plots_0909.Rmd
targeted attack and average neighbor degree analysis plots added

with open(f'data/interim/pcc_0909/pcc.pickle','rb') as f:
    e_pcc = pickle.load(f)
with open(f'data/interim/yuri/yuri.pickle','rb') as f:
    e_yuri = pickle.load(f)
with open(f'data/interim/huri/huri.pickle','rb') as f:
    e_huri = pickle.load(f)

pcc_df = e_pcc.df
yuri_df = e_yuri.df
huri_df = e_huri.df
```

```{r}
pcc_df = py$pcc_df
yuri_df = py$yuri_df
huri_df = py$huri_df
library(tidyverse)
library(cowplot)
library(ggpubr)
```

```{r}
p1 = ggplot(pcc_df, aes(x=deg,y=eff))+
    geom_point(aes(color=cat_))+
    xlab('Degree')+
    ylab('Effectiveness')+
    stat_cor(method='pearson')   +
    guides(color=guide_legend(title="Experiment categories"))+
    theme_bw()
p2 = ggplot(pcc_df, aes(x=deg,y=sens))+
    geom_point(aes(color=cat_))+
    xlab('Degree')+
    ylab('Sensitivity')+
    stat_cor(method='spearman')   +
    guides(color=guide_legend(title="Experiment categories"))+
    theme_bw()
lgn = cowplot::get_legend(p2)

@@

lgn34  <- cowplot::get_legend(p4)
    theme(axis.text.x=element_blank())
plot_grid(p1+theme(legend.position=''),
          p2+theme(legend.position=''),
          lgn,
          p3+theme(legend.position=''),
 p4+theme(legend.position=''), lgn34,
 nrow=2, labels=c('A','B','','C','D',''))
ggsave('tmp.png')
```

@@

deletion_lgn <- cowplot::get_legend(auc_plot)
plot_grid(deletion_plot+    theme(legend.position='')
, auc_plot+    theme(legend.position='')
,deletion_lgn, nrow=1, rel_widths =c(0.45, 0.45,.1), labels=c('A','B'))
ggsave('tmp.png',width=12)

@@

>>>>

with open(f'data/interim/pcc_0909/pcc.pickle','rb') as f:
    e_pcc = pickle.load(f)
with open(f'data/interim/yuri_0916/yuri.pickle','rb') as f:
    e_yuri = pickle.load(f)
with open(f'data/interim/huri_0916/huri.pickle','rb') as f:
    e_huri = pickle.load(f)

pcc_df = e_pcc.df
pcc_gc = e_pcc.graph_gc
pcc_gc_pos = (dict(pcc_gc.nodes(data='pos')))
yuri_df = e_yuri.df
huri_df = e_huri.df
```

```{r}
pcc_df = py$pcc_df%>%mutate(data='pcc')%>%mutate(sens_norm = sens/nrow(.))
yuri_df = py$yuri_df%>%mutate(data='yuri')%>%mutate(sens_norm = sens/nrow(.))
huri_df = py$huri_df%>%mutate(data='huri')%>%mutate(sens_norm = sens/nrow(.))

combined_df = bind_rows(pcc_df, yuri_df,huri_df)%>%
    mutate(data= fct_relevel(data, c('pcc','yuri','huri')))
library(tidyverse)
library(cowplot)
library(ggpubr)
```

```{r}
p1 = ggplot(pcc_df, aes(x=deg,y=eff))+
    geom_point(aes(color=cat_))+
    xlab('Degree')+
    ylab('Effectiveness')+
    stat_cor(method='pearson')   +
    guides(color=guide_legend(title="Experiment categories"))+
    theme_bw()
p2 = ggplot(pcc_df, aes(x=deg,y=sens_norm))+
    geom_point(aes(color=cat_))+
    xlab('Degree')+
    ylab('Sensitivity')+
    stat_cor(method='spearman')   +
    guides(color=guide_legend(title="Experiment categories"))+
    theme_bw()
lgn = cowplot::get_legend(p2)

@@

lgn34  <- cowplot::get_legend(p4)
    theme(axis.text.x=element_blank())
plot_grid(p1+theme(legend.position=''),
          p2+theme(legend.position=''),
          lgn,
          p3+theme(legend.position=''),
 p4+theme(legend.position=''), lgn34,
 nrow=2, labels=c('A','B','','C','D',''))
ggsave('reports/figures/paper_figures_0916/fig2.png')
```

@@

deletion_lgn <- cowplot::get_legend(auc_plot)
plot_grid(deletion_plot+    theme(legend.position='')
, auc_plot+    theme(legend.position='')
,deletion_lgn, nrow=1, rel_widths =c(0.45, 0.45,.1), labels=c('A','B'))
ggsave('reports/figures/paper_figures_0916/fig3.png',width=12)

@@

# Sensor connectivity and neighbor degree
```{r}
sensor_connectivity_df <- read_csv('data/interim/sensor_connectivity_0915/sensor_connectivity_df.csv')%>%
    mutate(data= fct_relevel(data, c('pcc','yuri','huri')))

#library(ggridges)

#sensor_connectivity_df %>%
#    filter(type=='random')%>%
#    ggplot(aes(x=ratio,y=data))+
##    facet_grid(rows=vars(data))+
##    geom_histogram(bins=50)
#    geom_density_ridges()
#ggsave('tmp.png',width=12)

#p3 = 
sensor_connectivity_plot <- 
    ggplot()+
    geom_boxplot(data=sensor_connectivity_df%>%filter(type=='random'),
                 aes(x=data,y=ratio,color=type))+
#    geom_jitter()+
    geom_point(data=sensor_connectivity_df%>%filter(type=='real'),
            aes(x=data,y=ratio,color=type, group=data))+
               #position=position_jitter(), aes(shape=data))+
    scale_color_discrete(labels=c('Random sampled set', 'Sensors'))+
    scale_x_discrete(labels=network_labels)+
  guides(color=guide_legend(title="Data type"),shape=guide_legend(title="Network type"))+
    xlab('Network type')+ylab('Ratio of between group edges\nto outgroup edges')+
    theme_bw()
neighbor_degree_plot <- combined_df%>%
    ggplot(aes(x=neighbor_degree,y=sens_norm))+
    facet_grid(rows=vars(data),labeller = labeller(data=facet_labels))+
    geom_point()+
    theme_bw()+
    xlab('Average neighbor degree')+
    ylab('Sensitivity')
plot_grid(neighbor_degree_plot, sensor_connectivity_plot, nrow=2 , labels=c('A','B'))
ggsave('reports/figures/paper_figures_0916/fig4.png')
